---
title: "Eliminating the Stigma Surrounding Mental Health"
author: "James Nguyen, Fengyuan Chen, Shradha Shankar"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%201.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%202.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%203.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/Aggregate%20Table%20Script.R")
source("calculate_summary_info.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Dynamic Paragraph
The summary information consists of calculations to better interpret the data. The first calculation is to figure out the maximum amount of cases and to do that this `r sprintf("%.2f", summury_info$Max_Cases)` was used. This is used as helpful information to understand the level of the problem and to also get a grasp of how prevalent the issue is. Leading to the next data point calculated, which is the district that the max cases is in represented by `r sprintf("%.2f", summury_info$Max_Cases_District)`. This is very important as there can be more research done on how to specifically improve certain resources to help mental health. It is also a great indicator of how certain resources are helping as it is possible to observe the resources available in the specific district that has the most cases. "BANGALORE URBAN' has the most cases and can be observed as to what is available. The Next calculation done is the calculation to see the highest amount of suicide cases, represented by `r sprintf("%.2f", summury_info$Highest_Suicide_Cases)`. This is very important as it is there to observe what vertain factors are contributing to this in which `r sprintf("%.2f", summury_info$Highest_Suicide_District)` helps determine which exact district has the highest amount of attempted suicide cases. This can help improve the mental health precaution and hopefully reduce this number. The last data point which is `r sprintf("%.2f", summury_info$highest_common_diagnosis_cases)` which is to calculate the highest number of common diagnosis cases. This can give a good representation of how prevalent this issue is for the common man with no predisposed medical conditions.





## Table

```{r table, echo=FALSE}
library(knitr)
kable(table, col.names = c("Age", "Socially Connected with People", "Meals Eaten on average"), caption = "How the connection with others have an impact on one's mental health:")
```
When looking at the state of students' mental health, it's important to consider how the connections with others impact a person's mental health and their habits. When we look at the correlations between the social connections and meals eaten on average per day, we notice a couple of trends. Those that are socially connected eat more on average compared to those that aren't socially connected. Those that struggle with their mental health seem to struggle more with unhealthier habits. Being socially connected to others can have a big impact on one's mental health and people's habits, whether it be with family or friends. We believe that building connections and relationships between students can have a positive impact on their mental health and some of their habits.  

## Chart 1: Methods of Self-Care
```{r chart1, echo=FALSE}
plot(chart_1)
```

This chart was included because I wanted to know the most popular ways in which
students tended to their mental health through self-care. We believe that 
there are many ways to take care of one's mental health that they can do either
at home or by themselves. This bar graph reveals the top 7 methods that people 
do to take care of their mental health. I also chose a horizontal bar graph to
make the groups more readable. In addition, I saw students liked listening to music,
playing video games, and more.

## Chart 2
```{r chart2, echo=FALSE}
plot(chart_2)
```

We decided to use a pie chart because we wanted to explore how one's GPA influences student's mental health brought by academic pressure. This pie chart depicts the relationship between student's CGPA and their mental health condition. It mainly uses  the 
column of three different mental conditions (depression, anxiety and panic attack) and CGPA. The final result shows that students with a higher CGPA normally are more likely to have one of these conditions. Maintaining a high GPA is hard and stressful.
