---
title: "Eliminating the Stigma Surrounding Mental Health"
author: "James Nguyen, Fengyuan Chen, Shradha Shankar"
date: "11/13/2021"
output: html_document
---

```{r setup, include=FALSE}
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%201.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%202.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/chart%203.R")
source("https://raw.githubusercontent.com/info201b-au2022/project-jam860/main/source/Aggregate%20Table%20Script.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Dynamic Paragraph






## Table

```{r table, echo=FALSE}
library(knitr)
kable(table, col.names = c("Age", "Socially Connected with People", "Meals Eaten on average"), caption = "How the connection with others have an impact on one's mental health:")
```
When looking at the state of students' mental health, it's important to consider how the connections with others impact a person's mental health and their habits. When we look at the correlations between the social connections and meals eaten on average per day, we notice a couple of trends. Those that are socially connected eat more on average compared to those that aren't socially connected. Those that struggle with their mental health seem to struggle more with unhealthier habits. Being socially connected to others can have a big impact on one's mental health and people's habits, whether it be with family or friends. We believe that building connections and relationships between students can have a positive impact on their mental health and some of their habits.  

## Chart 1: Methods of Self-Care
```{r chart1, echo=FALSE}
plot(chart_1)
```

This chart was included because I wanted to know the most popular ways in which
students tended to their mental health through self-care. We believe that 
there are many ways to take care of one's mental health that they can do either
at home or by themselves. This bar graph reveals the top 7 methods that people 
do to take care of their mental health. I also chose a horizontal bar graph to
make the groups more readable. In addition, I saw students liked listening to music,
playing video games, and more.

## Chart 2
```{r chart2, echo=FALSE}
plot(chart_2)
```

We decided to use a pie chart because we wanted to explore how one's GPA influences student's mental health brought by academic pressure. This pie chart depicts the relationship between student's CGPA and their mental health condition. It mainly uses  the 
column of three different mental conditions (depression, anxiety and panic attack) and CGPA. The final result shows that students with a higher CGPA normally are more likely to have one of these conditions. Maintaining a high GPA is hard and stressful.
